---
title: "Airbnb Case Study"
author: "ak5357"
date: "2024-10-08"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(p8105.datasets)
library(leaflet)
```


## Import Data
```{r}
# Import Data
data(nyc_airbnb) #import data
str(nyc_airbnb) #show structure

# Count room type
nyc_airbnb %>%
  count(room_type)

# Count neighborhoods
nyc_airbnb %>%
  count(neighbourhood_group)

```


**View Data.**
```{r}
nyc_airbnb |> 
  colnames()

nyc_airbnb |> view()
```

**Does rating vary by neighborhood, room type, or both?**
```{r}
# Does rating vary by neighborhood, room type, or both?
nyc_airbnb |> 
  group_by(neighbourhood_group) |> 
  summarize(
    avg_rating = mean(review_scores_location, na.rm = TRUE)
    )

nyc_airbnb |> 
  group_by(room_type) |> 
  summarize(
    avg_rating = mean(review_scores_location, na.rm = TRUE)
    )

nyc_airbnb |> 
  group_by(neighbourhood_group, room_type) |> 
  summarize(
    avg_rating = mean(review_scores_location, na.rm = TRUE)
    ) |> 
  arrange(avg_rating)

```


** Other Questions.**

* How is price related to other variables?
* Where are rentals located?
* Where are max and min airbnb prices?
  * What are average prices?
  * What factors affect prices?
* Where are prices going up and down over time?
* What's the relationship between number of reviews and average review?
* Does room type affect availability?
* What's the location of the unit?
  * What areas are popular?
  * Popularity = number of units? Average price?
* Are there repeat host?
  * If so, what does that mean?


## Leaflet

```{r}
pal = colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location
)

nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000
  ) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, color = ~ pal(review_scores_location), radius = 2)
```








